---
title: "Hands-On Exercise 6"
author: "Hsin Chieh Ma"
format: html
editor: visual
---

format can change here : pdf, html , docx

WorkShop-EP6-R

Installing and loading R packages

```{r}
#install package: pacman -> basic program R  function
#package in R
pacman::p_load(tidyverse, tidyquant, timetk)


```

Importing Singapore Company Data

```{r}

company <-read.csv("data/SGCompany.csv")
company

```

從網路上把 "company" 中的symbol的數據拿下來

```{r}
Stock_daily <- company %>%
  select(Symbol) %>%
  tq_get(get ="stock.prices",
         from = "2022-01-01",
         to = "2022-12-31")
```

把兩個table company combine在一起

```{r}
Stock_data <- Stock_daily %>%
  left_join(company)
```

close = closing price

geom_line() =\>把線畫出來

labs =\> 改表格名字

theme_tq() = belong to tidyquant -\> give you the. whole structure -\> tickline-\> 改顏色(主題而已),沒有也沒關係

```{r}
Stock_data %>%
  filter(Name == "DBS Group") %>%
  ggplot(aes(x = date, y = close)) +
    geom_line() +
    labs(title = "DBS Group Holdings Ltd (DBSDF) Daily Stock Price",
         y = "Closing Price", x = "") +
    theme_tq()
```

facet_ncol = 表格打算怎麼排放 (一行2個)

facet_scale = 價格的range

interactive = 鼠標上去的時候 會有反應

blue line = moving avg curve (30Days)

```{r}
Stock_data %>%
  group_by(Name) %>%
  plot_time_series(date, close,
                   .facet_ncol   = 2,
                   .facet_scales = "free",
                   .interactive  = TRUE)
```

```{r}
end <- as_date("2022-06-30")
start <- end - weeks(2)
Stock_data %>%
  filter(Name == "DBS Group") %>%
  filter(date >= start - days(2 * 15)) %>%
ggplot(aes(x=date, y=close)) +
  geom_candlestick(aes(open=open,
                       high=high,
                       low=low,
                       close=close)) +
                       labs(title = "Daily stock prices of DBS Group") +
  coord_x_date(xlim = c(start, end)) +
  theme_tq()
```

還有一次很多圖表的\*

需要自己寫\*

MA的R寫法

```{r}
Stock_data %>%
  filter(Symbol == "D05.SI") %>%
  filter(date >= start - days(2 * 15)) %>%
  ggplot(aes(x = date, y = close)) +
  geom_candlestick(aes(open = open, high = high, low = low, close = close)) +
  geom_ma(ma_fun = SMA, n = 5, linetype = 5, size = 1.25) +
  geom_ma(ma_fun = SMA, n = 15, color = "red", size = 1.25) +
    labs(title = "DBS Group Holdings Ltd Daily Stock Price",
         subtitle = "5 and 15-Day SMA",
         y = "Closing Price", x = "") +
    coord_x_date(xlim = c(end - weeks(5), end)) +
                   theme_tq()
```

```{r}
SGBank <- read_csv("data/SGBank.csv")

```

```{r}
SGBank_daily <- SGBank %>%
  select(Symbol) %>%
  tq_get(get = "stock.prices",
         from = "2020-04-01",
         to = "2022-06-30")
```

```{r}
SGBank_returns_monthly  <- SGBank_daily %>%
group_by(Symbol) %>%
tq_transmute(select = adjusted,
mutate_fun = periodReturn,
period = "monthly",
col_rename = "Ra")
```

```{r}
SGBank_returns_monthly
```

```{r}
wts <- c(0.4, 0.3, 0.3)
porfolio_returns_monthly <- SGBank_returns_monthly %>%
  tq_portfolio(assets_col = Symbol,
               returns_col = Ra,
               weights = wts,
               col_rename = "Ra")
```

```{r}
ggplot(data = porfolio_returns_monthly,
       aes(x = date, y = Ra)) +
  geom_bar(stat = "identity",
           fill = palette_light()[[1]]) +
  labs(title = "Porfoli Returns",
       subtitle = "40% DBS, 30% OCBC and 30% UOB",
       caption = "Shows an above zero trend meaning
       positive returns",
       x = "", y = "Monthly Returns") +
  geom_smooth(method = "lm") +
  theme_tq() +
  scale_color_tq() +
  scale_y_continuous(labels = scales::percent)
```

```{r}
wts <- c(0.4, 0.3, 0.3)
portfolio_growth_monthly <- SGBank_returns_monthly %>%
  tq_portfolio(assets_col = Symbol,
               returns_col = Ra,
               weights = wts,
               col_rename = "investment.growth",
               wealth.index = TRUE) %>%
  mutate(investment.growth = investment.growth * 100000)
```
