---
title: "Assignment -- Linear Regression"
author: "Ma Hsin Chieh"
output:
  html_document:
    theme: readable
    df_print: paged
---


### Problem Statement


In this exercise, we are interested in predicting a patient's length of stay (LOS) in the intensive care unit (ICU) using his or her demographic information and the worst reading of critical clinical variables during the first 24-hour stay in the ICU. We will use the data contained in the file "Assignment_Linear_Regression_Data_Train.csv" to build models, and "Assignment_Linear_Regression_Data_Test.csv" will be used in out-of-sample validation. 






### Questions

```{r}

#install the package
library(dplyr)
# load csv
train = read.csv("Assignment_Linear_Regression_Data_Train.csv")
str(train)
# find the avg of the table
summary(train)

df <-data.frame(Q1=c(train$Gender))
df %>% count(Q1)

#another way of doing calculation
male <- subset(train, Gender =="Male")
precentage_male = nrow(male)/nrow(train)
precentage_male

```


1. Load and explore the training data file, check summary statistics of all the variables, and answer the following questions.

    i) What is the average age of the patients?
    59.57
     
    ii) What is the percentage of male patients?
    72.3%

2. Build a linear regression model to predict the LOS using vital signs (check the data description file to identify the list of vital signs). Use the training set to build the model.

```{r}
model1 = lm(LOS~Temperature+ RespirationRate+ HeartRate + SystolicBP + DiastolicBP + SpO2, data = train)
summary(model1)

```


    i) What is the linear regression equation produced by your model? Make sure to give the coefficients for each of the independent variables.
    
    LOS = -0.02745 Temperature - 0.56502 RespirationRate + 0.29940 HeartRate - 0.46818 SystolicBP - 1.40764 DiastolicBP - 1.77067 SpO2
     
    ii) What is the $R^2$ of the model?
    
    0.02237
     
    iii) Which variables are significant? We consider a variable significant only if its *p*-value is below 0.05.
    only DiastolicBP is significant

    

3. We want to improve our linear regression model by including all the variables in the analysis. 


```{r}
model2 = lm(LOS~Age + Gender + Race + Temperature+ RespirationRate+ HeartRate + SystolicBP + DiastolicBP + SpO2 + Haemoglobin + NumWBC + ArterialpO2 + Creatinine + Urea + GCS , data = train)

summary(model2)

model3 = lm(LOS~ ArterialpO2 + Creatinine + Urea + GCS , data = train)

summary(model3)
```


    i) What is the $R^2$ of the new model?
    
    0.08234
     
    ii) Which variables are significant? We consider a variable significant only if its *p*-value is below 0.05. Build another linear regression model using only these significant variables. What is the $R^2$ of this model?
    
    ArterialpO2 , Creatinine , Urea , GCS
    0.07561
    
    iii) What do you think about the accuracy and values of the model?
    
    R-square only 7.5%, which means the linear regression model can only explained 7.5% of the variation dat, is not that useful. Can not explained the data


4. We want to test the performance of our models using the test data set. 

```{r}
test = read.csv("Assignment_Linear_Regression_Data_Test.csv")
str(test)

#count for all variables 
predictTest2 = predict(model2, newdata = test)

SSE2 = sum((test$LOS - predictTest2)^2)
SST2 = sum((test$LOS - mean(train$LOS))^2)
R2 = (1 - SSE2/SST2)
# the out-of-sample R^2
R2


#count for only vital signs
predictTest1 = predict(model1, newdata = test)

SSE1 = sum((test$LOS - predictTest1)^2)
SST1 = sum((test$LOS - mean(train$LOS))^2)
R1 = (1 - SSE1/SST1)
# the out-of-sample R^2
R1

```


    i) What is the out-of-sample $R^2$ of the model using all the variables? Please check carefully how the out-of-sample $R^2$ is computed in the lecture note for the wine case study. Note that the benchmark baseline model is still the historical average price of the training data set, not the average price of the test data set. The point here is that the benchmark model also does not know the future, and it cannot use the future average price to predict the future. 
    -0.03569267
    
    ii) What is the out-of-sample $R^2$ of our first model using only vital signs?
    0.09480606
